\documentclass[10pt]{article}
\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=5mm,
bottom=5mm
 }

\usepackage{lineno}
\linenumbers

\usepackage{enumitem}
\setlist{nolistsep}

\title{Attitudes to advertising in Mexico} 
\author{Miguel P Xochicale \\
Report 01, Version 01}
\date{11th February 2018}

\begin{document}
\maketitle
\thispagestyle{empty} %No number


\section{Writing Activity}
\textit{
An international market research company has asked you to write a report
on advertising in your country. The company that has commissioned the 
report wants to know about the most common approaches used and how 
consumers respond to them. You are also asked to suggest changes to 
current approaches or alternative approaches which you belive would
be more effective.
}
\\
Write your report in 220-260 words in an appropriate style.

\section{Report}
\subsection{Introduction}

Undoubtedly, Mexico is a country where marketing strategies of any 
international company can be seriously put into a test, the reason for that
is because of the diversity of both cultural and economical background of 
Mexicans. With that in mind, this report presents a list three markets 
to give a gist of traditional and common approaches for advertising
in Mexico. 
In addition to the customers' reaction to each of the markets, 
we finalise the report with a list of  recommendations that aim 
to create a more effective impact on people with advertisements.

%Telemarketing? Advertising hoardings? Junk mail? TV advertising? Internet pop-ups? Giveaways in magazines?


\subsection{Types of Mexican Commercial Markets}
Examples of commercial Mexican markets are many but in this report,
we are focusing  on the markets that, from my view, generate a 
major economical gain in the last ten years. 
In each one of the following examples, it is provided information about 
traditional approaches for marketing and a general responses of the customers.
\begin{itemize}
\item Education. The advertisement, specifically, in private universities 
is well made, as investments in this regard are highly relevant for such 
institutions.
For instance, advertisements goes from TV commercials, internet pop-ups,
or even the well known open days where students visits the installations.
However, public universities rely on less sophisticated approaches such 
as flyers, spots in radio and mainly on word of mouth and personal 
views of the ex-graduates.
\item Gastronomy. Advertising in this area is particularly special,
as the Mexican markets have many informal commerce, one of them being gastronomy.
Essentially, what it works best is word of mouth advertising than any of the 
other options. However, for restaurants or big supermarkets
TV advertisings and internet pop ups is the main way to attract people.
\item Tourism. This area is typically advertised by TV commercials
 and customers essentially rely on how well is presented in the video. 
However, customers, specially national ones, usually know someone 
who had been there and then from viva voice, customers are convinced 
to visit determined place.
\end{itemize}

\subsection{Recommendations}
Generally speaking, word of mouth advertising is crucial to sell well
in typical Mexican markets and I hardly doubt that changes can be made
in this regard since these informal way of advertising is rooted in 
the cultural background of Mexicans. However, the following
emerging technologies can be proposed to improve the way different 
products are advertised in the Mexican market:
\begin{itemize}
\item Virtual reality (VR) can be beneficial for virtual tours
for either a visit to the installations of an institution
or a view to a tourist resort.
\item Cripto currencies can be a helpful way to attract younger
costumers who are more likely to go on a holiday where 
any transaction can be made with the use of digital currencies.
\end{itemize}

\subsection{Conclusions}
Nonetheless, these technologies might not be appropriate
for every Mexican customer in the previous examples.
But, in my view, it is a good time to start with the use of 
these emerging technologies and create conditions where
win-win situations can be created and everyone can be 
benefited from this as a customer, creator of technologies or 
anyone in the marketing companies.
\end{document}
